### 2014-09-10 RFCs/HDF5/VOL/user_guide/plugin.tex
UG updates
Former-commit-id: b80e6f020c627d40056087212ea138ffcacb3d5f

The {\tt set\_extent} callback in the dataset class should extend the
dataset dimensions and returns an {\tt herr\_t} indicating success or
failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*set_extent)(void *dset, const hsize_t size[], 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt dset} & (IN): Pointer to the dataset object.\\
  {\tt size} & (IN): new dimensions of the dataset.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

@@

\begin{lstlisting}
typedef struct H5VL_datatype_class_t {
    void *(*commit)(void *obj, H5VL_loc_params_t loc_params, 
        const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, 
        hid_t tapl_id, hid_t dxpl_id, void **req);

    void *(*open) (void *obj, H5VL_loc_params_t loc_params, 
        const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);

    ssize_t (*get_binary)(void *obj, unsigned char *buf, size_t size, 
        hid_t dxpl_id, void **req);

    herr_t (*get) (void *obj, H5VL_datatype_get_t get_type, 
        hid_t dxpl_id, void **req, va_list arguments);

    herr_t (*close) (void *dt, hid_t dxpl_id, void **req);
} H5VL_datatype_class_t;
\end{lstlisting}

@@

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all datatype get API routines */
typedef enum H5VL_datatype_get_t {
    H5VL_DATATYPE_GET_TCPL   /*datatype creation property list */
} H5VL_datatype_get_t;
\end{lstlisting}

@@

\begin{itemize}
\item {\tt H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
  creation property list:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    type creation property list.
  \end{enumerate}
\end{itemize}

@@

\begin{lstlisting}
typedef struct H5VL_object_class_t {
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
        H5I_type_t *opened_type, hid_t dxpl_id, void **req);

    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, 
        const char *src_name, void *dst_obj, 
        H5VL_loc_params_t loc_params2, const char *dst_name,
        hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);

    herr_t (*visit)(void *obj, H5VL_loc_params_t loc_params, 
        H5_index_t idx_type, H5_iter_order_t order, 
        H5O_iterate_t op, void *op_data, hid_t dxpl_id, void **req);

    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_get_t get_type, hid_t dxpl_id, 
        void **req, va_list arguments);

    herr_t (*misc)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_misc_t misc_type, hid_t dxpl_id, 
        void **req, va_list arguments);

    MSC - NOT USED
    herr_t (*optional)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_optional_t op_type, hid_t dxpl_id, 
        void **req, va_list arguments);

    MSC - NOT USED
    herr_t (*close) (void *obj, H5VL_loc_params_t loc_params, 
        hid_t dxpl_id, void **req);
} H5VL_object_class_t;
\end{lstlisting}

@@

The {\tt visit} callback in the object class should recursively visit
all objects accessible from a specified object and call the
user defined function on each one. It returns an {\tt herr\_t}
indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*visit)(void *obj, H5VL_loc_params_t loc_params, 
        H5_index_t idx_type, H5_iter_order_t order, 
        H5O_iterate_t op, void *op_data, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the iteration needs
  to happen or where the look-up of the target object needs to
  start.\\
  {\tt loc\_params} & (IN): The location parameters as
  explained in section~\ref{sec:map}. The type could be {\tt
    H5VL\_OBJECT\_BY\_SELF} or {\tt
    H5VL\_OBJECT\_BY\_NAME} for this callback.\\
  {\tt idx\_type} & (IN): Type of index.\\
  {\tt order} & (IN): Order in which to iterate over index.\\
  {\tt op} & (IN): User-defined function to pass each object to.\\
  {\tt op\_data} & (IN/OUT): User data to pass through to and to be
  returned by iterator operator function. \\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

@@

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all object get API routines */
typedef enum H5VL_object_get_t {
    H5VL_OBJECT_EXISTS,      /* Object exists?       */
    H5VL_OBJECT_GET_INFO,    /* object info          */
    H5VL_OBJECT_GET_COMMENT, /* object comment       */
    H5VL_REF_GET_REGION,     /* dataspace of region  */
    H5VL_REF_GET_TYPE,       /* type of object       */
    H5VL_REF_GET_NAME        /* object name          */
} H5VL_object_get_t;
\end{lstlisting}

@@

\begin{itemize}
\item {\tt H5VL\_OBJECT\_EXISTS}, to check if an object with name
  specified in {\tt loc\_params} (type {\tt H5VL\_OBJECT\_BY\_NAME})
  exists:
  \begin{enumerate}
  \item {\tt htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_GET\_INFO}, to retrieve object info:
  \begin{enumerate}
  \item {\tt H5O\_info\_t *oinfo} (OUT): info structure to fill the
    object info in.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_GET\_COMMENT}, to retrieve the comment on the
  object specified with {\tt obj} and {\tt loc\_params} which could
  have types {\tt H5VL\_OBJECT\_BY\_SELF} or {\tt
    H5VL\_OBJECT\_BY\_NAME} here:
  \begin{enumerate}
  \item {\tt void *} (OUT): Buffer to store the comment in.
  \item {\tt size\_t buf\_size} (IN): the size of the buffer passed in.
  \item {\tt ssize\_t *ret} (OUT): return the actual size needed
    to store the comment.
  \end{enumerate}

@@

\item {\tt H5VL\_REF\_GET\_TYPE}, to retrieve object type a reference
  points to:
  \begin{enumerate}
  \item {\tt H5O\_type\_t *type} (OUT): buffer to return the object type.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
    query.
  \item {\tt void *ref} (IN): the region reference to query.
  \end{enumerate}

\item {\tt H5VL\_REF\_GET\_NAME}, to retrieve a name for a referenced object:
  \begin{enumerate}
  \item {\tt ssize\_t *ret} (OUT): buffer to return the length of the
    name.
  \item {\tt char* name} (OUT): buffer to copy the name into.
  \item {\tt size\_t size} (IN): size of the buffer name, if 0, return
    only the buffer size needed.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
    query.
  \item {\tt void *ref} (IN): the region reference to query.
  \end{enumerate}
\end{itemize}

The {\tt misc} callback in the object class should execute operations
in the container on objects as specified in the {\tt misc\_type}
parameter.It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*misc)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_misc_t misc_type, hid_t dxpl_id, 
        void **req, va_list arguments);
\end{lstlisting}

The {\tt misc\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all object general operations */
typedef enum H5VL_object_misc_t {
    H5VL_ATTR_RENAME,               /* H5Arename                 */
    H5VL_OBJECT_CHANGE_REF_COUNT,   /* H5Oincr/decr_refcount     */
    H5VL_OBJECT_SET_COMMENT,        /* H5Oset_comment(_by_name)  */
    H5VL_REF_CREATE                 /* H5Rcreate                 */
} H5VL_object_misc_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): A location object for the operation.\\
  {\tt loc\_params} & (IN): The location parameters as
  explained in section~\ref{sec:map}.\\
  {\tt misc\_type} & (IN): The type of the operation.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the misc operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt misc\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_ATTR\_RENAME}, to rename an attribute under the
  location object where the {\tt loc\_params} could have types {\tt
    H5VL\_OBJECT\_BY\_SELF} or {\tt H5VL\_OBJECT\_BY\_NAME}:
  \begin{enumerate}
  \item {\tt char *old\_name} (IN): old name of the attribute to
    rename.
  \item {\tt char *new\_name} (IN): the new attribute name to set for
    the attribute.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
  count for the object in {\tt obj}:
  \begin{enumerate}
  \item {\tt int ref\_count} (IN): reference count to set on the object.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_SET\_COMMENT}, to set a comment on the object
  where the {\tt loc\_params} could have types {\tt
    H5VL\_OBJECT\_BY\_SELF} or {\tt H5VL\_OBJECT\_BY\_NAME}:
  \begin{enumerate}
  \item {\tt char *comment} (IN): comment to set on the object.
  \end{enumerate}

@@

\begin{lstlisting}
typedef struct H5VL_link_class_t {
    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj,
        H5VL_loc_params_t loc_params, hid_t lcpl_id, 
        hid_t lapl_id, hid_t dxpl_id, void **req);

    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1,
        void *dst_obj, H5VL_loc_params_t loc_params2,
        hbool_t copy_flag, hid_t lcpl, hid_t lapl, 
        hid_t dxpl_id, void **req);

    herr_t (*iterate)(void *obj, H5VL_loc_params_t loc_params, 
        hbool_t recursive, H5_index_t idx_type, H5_iter_order_t order, 
        hsize_t *idx, H5L_iterate_t op, void *op_data, hid_t dxpl_id, 
        void **req);

    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_link_get_t get_type, hid_t dxpl_id, void **req, 
        va_list arguments);

    herr_t (*remove)(void *obj, H5VL_loc_params_t loc_params, 
        hid_t dxpl_id, void **req);
} H5VL_link_class_t;
\end{lstlisting}

@@

The {\tt move} callback in the link class should copy or move a link
within the HDF5 container. It returns an {\tt herr\_t} indicating
success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1,
        void *dst_obj, H5VL_loc_params_t loc_params2,
        hbool_t copy_flag, hid_t lcpl, hid_t lapl, 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt src\_obj} & (IN): original/source object or file. \\
  {\tt loc\_params1} & (IN): The location parameters for the source
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  {\tt dst\_obj} & (IN): destination object or file. \\
  {\tt loc\_params1} & (IN): The location parameters for the destination
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  {\tt copy\_flag} & (IN): flag to indicate whether link is to be
  copied (value 1) or moved (value 0).\\
  {\tt lcpl\_id} & (IN): The link creation property list.\\
  {\tt lapl\_id} & (IN): The link access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt iterate} callback in the link class should iterate over links
in a group and apply a user defined routine. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*iterate)(void *obj, H5VL_loc_params_t loc_params, 
        hbool_t recursive, H5_index_t idx_type, H5_iter_order_t order, 
        hsize_t *idx, H5L_iterate_t op, void *op_data, hid_t dxpl_id, 
        void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): object where to start iteration or where the
  lookup for the target object needs to start. \\
  {\tt loc\_params} & (IN): The location parameters for the source
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} or {\tt H5VL\_OBJECT\_BY\_SELF} in this
  callback.\\ 
  {\tt recursive} & (IN): whether to recursively follow links into
  subgroups of the specified group.\\
  {\tt idx\_type} & (IN): Type of index which determines the order.\\
  {\tt idx} & (IN/OUT): iteration position where to start and return
  position where an interrupted iteration may restart.\\
  {\tt op} & (IN): User-defined function for the iterator.\\
  {\tt op\_data} & (IN/OUT): User data to pass through to and to be
  returned by iterator operator function.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

@@

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all link get API routines */
typedef enum H5VL_link_get_t {
    H5VL_LINK_EXISTS,          /* link existence  */
    H5VL_LINK_GET_INFO,        /* link info       */
    H5VL_LINK_GET_NAME,        /* link name       */
    H5VL_LINK_GET_VAL          /* link value      */
} H5VL_link_get_t;
\end{lstlisting}

@@

\begin{itemize}
\item {\tt H5VL\_LINK\_EXITS}, to determine whether the link specified
  in the {\tt loc\_params} exits ({\tt loc\_params} is of type {\tt
    H5VL\_OBJECT\_BY\_NAME} only with this type):
  \begin{enumerate}
  \item {\tt htri\_t *ret} (OUT): buffer for the existence of the link
    (0 for no, 1 for yes).
  \end{enumerate}

\item {\tt H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
  link specified in the {\tt loc\_params}:
  \begin{enumerate}
  \item {\tt H5L\_info\_t linfo} (OUT): pointer to info structure to
    fill.
  \end{enumerate}

@@

\item {\tt H5VL\_LINK\_GET\_VAL}, to retrieve the link value from the
  link specified in the {\tt loc\_params}:
  \begin{enumerate}
  \item {\tt void *buf} (OUT): buffer to put the value into.
  \item {\tt size\_t size} (IN): size of the passed in buffer.
  \end{enumerate}

The {\tt remove} callback in the link class should remove a link from
an HDF5 container, and returns an {\tt herr\_t} indicating success or
failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*remove)(void *obj, H5VL_loc_params_t loc_params, 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): group object or file containing the link.\\
  {\tt loc\_params} & (IN): The location parameters for the link to be
  deleted.The type can be only {\tt H5VL\_OBJECT\_BY\_NAME} or {\tt
    H5VL\_OBJECT\_BY\_IDX} in this callback.\\ 
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

@@

\begin{lstlisting}
typedef struct H5VL_async_class_t {
    herr_t (*cancel)(void **, H5ES_status_t *);

    herr_t (*test)  (void **, H5ES_status_t *);

    herr_t (*wait)  (void **, H5ES_status_t *);
} H5VL_async_class_t;
\end{lstlisting}

@@

>>>>

@@

\begin{lstlisting}
typedef struct H5VL_datatype_class_t {
    void *(*commit)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
    herr_t (*get)   (void *obj, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*specific)(void *obj, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*close) (void *dt, hid_t dxpl_id, void **req);
} H5VL_datatype_class_t;
\end{lstlisting}

@@

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for datatype GET callback */
typedef enum H5VL_datatype_get_t {
    H5VL_DATATYPE_GET_BINARY,               /* get serialized form of transient type */
    H5VL_DATATYPE_GET_TCPL                  /* datatype creation property list     */
} H5VL_datatype_get_t;
\end{lstlisting}

@@

\begin{itemize}
\item {\tt H5VL\_DATATYPE\_GET\_BINARY}, to retrieve the serialized original transient HDF5 datatype that was committed, or
return the size that is required for it be serialized if the passed in buffer is {\tt NULL}. The HDF5 library provides two functions to
encode and decode datatypes in their transient form, {\tt H5Tencode()} and {\tt H5Tdecode()}. When a datatype is committed, the plugin is required to keep the serialized form of the transient datatype stored somewhere in the container (which is usually the case anyway when committing a named datatype), so it can be retrieved with this call. This is needed to generate the higher level HDF5 datatype identifier that allows all the H5T ``transient'' routines to work properly on the named datatype.
  \begin{enumerate}
  \item {\tt ssize\_t *nalloc} (OUT): buffer to store the total size of the serialized datatype.
  \item {\tt void *buf} (OUT): buffer to store the serialized datatype.
  \item {\tt size\_t size} (IN): size of the passed in buffer.
  \end{enumerate}

\item {\tt H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
  creation property list:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    type creation property list.
  \end{enumerate}
\end{itemize}

The {\tt specific} callback in the datatype class currently does not require any functionality to be implemented and should be left as {\tt NULL}.

@@

\begin{lstlisting}
typedef struct H5VL_object_class_t {
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, const char *src_name, void *dst_obj, H5VL_loc_params_t loc_params2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
} H5VL_object_class_t;
\end{lstlisting}

@@

@@

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
r object GET callback */
typedef enum H5VL_object_get_t {
    H5VL_REF_GET_NAME,                 /* object name                       */
    H5VL_REF_GET_REGION,               /* dataspace of region               */
    H5VL_REF_GET_TYPE                  /* type of object                    */
} H5VL_object_get_t;
\end{lstlisting}

@@

\begin{itemize}
\item {\tt H5VL\_REF\_GET\_NAME}, to retrieve a name for a referenced object:
  \begin{enumerate}
  \item {\tt ssize\_t *ret} (OUT): buffer to return the length of the
    name.
  \item {\tt char* name} (OUT): buffer to copy the name into.
  \item {\tt size\_t size} (IN): size of the buffer name, if 0, return
    only the buffer size needed.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
    query.
  \item {\tt void *ref} (IN): the region reference to query.
  \end{enumerate}

@@

\item {\tt H5VL\_REF\_GET\_TYPE}, to retrieve object type a reference
  points to:
  \begin{enumerate}
  \item {\tt H5O\_type\_t *type} (OUT): buffer to return the object type.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
    query.
  \item {\tt void *ref} (IN): the region reference to query.
  \end{enumerate}
\end{itemize}

The {\tt specific} callback in the object class implements specific operations on HDF5 objects as specified in the {\tt
  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

The {\tt specific\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for object SPECIFIC callback */
typedef enum H5VL_object_specific_t {
    H5VL_OBJECT_CHANGE_REF_COUNT,      /* H5Oincr/decr_refcount              */
    H5VL_OBJECT_EXISTS,                /* H5Oexists_by_name                  */
    H5VL_OBJECT_VISIT,                 /* H5Ovisit(_by_name)                 */
    H5VL_REF_CREATE                    /* H5Rcreate                          */
} H5VL_object_specific_t;
\end{lstlisting}

\begin{itemize}
\item {\tt H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
  count for the object in {\tt obj}:
  \begin{enumerate}
  \item {\tt int ref\_count} (IN): reference count to set on the object.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_EXISTS}, to check if an object with name
  specified in {\tt loc\_params} (type {\tt H5VL\_OBJECT\_BY\_NAME})
  exists:
  \begin{enumerate}
  \item {\tt htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_VISIT}, to iterate over all objects starting at the location provided and call a user specified callback on each one:
  \begin{enumerate}
  \item {\tt H5\_index\_t idx\_type} (IN): Type of index.\\
  \item {\tt H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
  \item {\tt H5O\_iterate\_t op} (IN): User-defined function to pass each object to. \\
  \item {\tt void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
  \end{enumerate}

@@

\begin{lstlisting}
typedef struct H5VL_link_class_t {
    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj, H5VL_loc_params_t loc_params, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
} H5VL_link_class_t;
\end{lstlisting}

@@

The {\tt move} callback in the link class should move a link within the HDF5 container. It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt src\_obj} & (IN): original/source object or file. \\
  {\tt loc\_params1} & (IN): The location parameters for the source
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  {\tt dst\_obj} & (IN): destination object or file. \\
  {\tt loc\_params1} & (IN): The location parameters for the destination
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  {\tt lcpl\_id} & (IN): The link creation property list.\\
  {\tt lapl\_id} & (IN): The link access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt copy} callback in the link class should copy a link within the HDF5 container. It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt src\_obj} & (IN): original/source object or file. \\
  {\tt loc\_params1} & (IN): The location parameters for the source
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  {\tt dst\_obj} & (IN): destination object or file. \\
  {\tt loc\_params1} & (IN): The location parameters for the destination
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  {\tt lcpl\_id} & (IN): The link creation property list.\\
  {\tt lapl\_id} & (IN): The link access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

@@

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all link get API routines */
typedef enum H5VL_link_get_t {
    H5VL_LINK_GET_INFO,        /* link info       */
    H5VL_LINK_GET_NAME,        /* link name       */
    H5VL_LINK_GET_VAL          /* link value      */
} H5VL_link_get_t;
\end{lstlisting}

@@

\begin{itemize}
\item {\tt H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
  link specified in the {\tt loc\_params}:
  \begin{enumerate}
  \item {\tt H5L\_info\_t linfo} (OUT): pointer to info structure to
    fill.
  \end{enumerate}

@@

\item {\tt H5VL\_LINK\_GET\_VAL}, to retrieve the link value from the
  link specified in the {\tt loc\_params}:
  \begin{enumerate}
  \item {\tt void *buf} (OUT): buffer to put the value into.
  \item {\tt size\_t size} (IN): size of the passed in buffer.
  \end{enumerate}
\end{itemize}

The {\tt specific} callback in the link class implements specific operations on HDF5 links as specified in the {\tt
  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

The {\tt specific\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for link SPECIFIC callback */
typedef enum H5VL_link_specific_t {
    H5VL_LINK_DELETE,          /* H5Ldelete(_by_idx)                */
    H5VL_LINK_EXISTS,          /* link existence                    */
    H5VL_LINK_ITER             /* H5Literate/visit(_by_name)              */
} H5VL_link_specific_t;
\end{lstlisting}

\begin{itemize}
\item {\tt H5VL\_LINK\_DELETE}, to remove a link specified in the location parameter from an HDF5 container.

\item {\tt H5VL\_LINK\_EXITS}, to determine whether the link specified
  in the {\tt loc\_params} exits ({\tt loc\_params} is of type {\tt
    H5VL\_OBJECT\_BY\_NAME} only with this type):
  \begin{enumerate}
  \item {\tt htri\_t *ret} (OUT): buffer for the existence of the link
    (0 for no, 1 for yes).
  \end{enumerate}

\item {\tt H5VL\_LINK\_ITER}, to iterate over all links starting at the location provided and call a user specified callback on each one:
  \begin{enumerate}
  \item {\tt hbool\_t recursive} (IN): whether to recursively follow links into subgroups of the specified group.\\
  \item {\tt H5\_index\_t idx\_type} (IN): Type of index.\\
  \item {\tt H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
  \item {\tt hsize\_t *idx} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
  \item {\tt H5L\_iterate\_t op} (IN): User-defined function to pass each link to. \\
  \item {\tt void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
  \end{enumerate}
\end{itemize}

@@

\begin{lstlisting}
typedef struct H5VL_async_class_t {
    herr_t (*cancel)(void **, H5ES_status_t *);
    herr_t (*test)  (void **, H5ES_status_t *);
    herr_t (*wait)  (void **, H5ES_status_t *);
} H5VL_async_class_t;
\end{lstlisting}

@@

\subsection{The Optional Generic Callback}
A generic optional callback is provided for services that are specific to a plugin. Asynchronous operations/services could have been implemented through this optional callback, however since we anticipate asynchronous operations to be common across many plugins, they have been promoted to a subclass by themselves as shown in the previous section. Other services that are not shared across different plugins might include transactional semantics for managing operations like in~/ref{fastforward}, MSC - add more use cases here.

The {\tt optional} callback has the following definition. It returns an {\tt herr\_t} indicating success or failure.
